%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Previous Research Positions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
 \cventry
        {Supervisors: Andres Moreno \& Aaron Ragsdale} % which lab
        {Graduate Reaseracher} % Title
        {CINVESTAV LANGEBIO, Irapuato Mx} % Where?
        {2020 - Present} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
            Computational genomics and population genetics.
          \end{flushleft}
            }
          \end{cvitems}
        }

%---------------------------------------------------------
 \cventry
        {Principal Investigator: Ariel Bazzini} % which lab
        {Bioinformatician} % Title
        {Stowers Institute, Kansas City, USA} % Where?
        {2017 - 2020} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
            I continued as bioinformatician in the lab of Ariel Bazzini. I studied how gene regulatory information is encoded in the coding DNA sequence 
            through a mechanism known as codon optimality.
          \end{flushleft}
            }
          \end{cvitems}
        }

%---------------------------------------------------------
 \cventry
        {Principal Investigator: Ariel Bazzini} % which lab
        {Undergraduate Research Thesis} % Title
        {Stowers Institute, Kansas City, USA} % Where?
        {2016 - 2017} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
              I worked in the bazzini lab for my undergraduate thesis project
              entitle: The regulatory grammar of codon optimality.
          \end{flushleft}
            }
          \end{cvitems}
        }
%---------------------------------------------------------
 \cventry
        {Principal Investigator: Julia Zeitlinger} % which lab
        {Stowers summer scholar} % Title
        {Stowers Institute, Kansas City, USA} % Where?
        {Summer 2015} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
              I develop a pipeline to analyze protein DNA binding interactions
              with ChiP-nexus data.
          \end{flushleft}
            }
          \end{cvitems}
        }
%---------------------------------------------------------
 \cventry
        {Principal Investigator: Cei Abreu-Goodgear} % which lab
        {Undergraduate summer research} % Title
        {CINVESTAV LANGEBIO, Irapuato Mx} % Where?
        {Summer 2014} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
              I studied the conservation of micro-RNAs targets in different
              vertebrates species using RNA-seq data.
          \end{flushleft}
            }
          \end{cvitems}
        }
%---------------------------------------------------------
\cventry
        {$\;$} % collaborators
        {Research interests} % Title
        {$\;$} % Journal
        {$\;$} % Date
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
            \begin{flushleft}
              \textit{I am interested in transitioning into evolutionary biology.
              Specifically, I find the parallels between population genetics and
              mathematics extremely intriguing. I am therefore
              interested in using my background on computational genomics,
              statistical inference, and mathematics to explore
              questions on \textbf{theoretical population genetics} and \textbf{human evolution}.}
          \end{flushleft}
            }
          \end{cvitems}
        }
        
%---------------------------------------------------------
\end{cventries}
